A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-31 4_method.tex
merged and redo significance properties figures

\begin{figure} \centering
\begin{subfigure}{0.45\columnwidth} \centering
\includegraphics[height=.7\columnwidth]{sources/method/distance_based_angles.pdf}
\caption{Significance}
\label{distance_based_angles}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth} \centering
\includegraphics[height=.7\columnwidth]{sources/method/distance_ratio_limit.pdf}
\caption{Distance}
\label{distance_ratio_limit}
\end{subfigure}
\caption{
Properties of feature radius $R$.
Part of outline shape in thick black,
skeleton in red,
inscribed circle in gray,
radii in dashed lines.
The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
}
\end{figure}

@@

\begin{lemma}\label{single_upward_edge}
From any node in the graph which is not a saddle point there is at most a single edge going upward.
\end{lemma}
\begin{proof}
Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_1, p_2, p_3$.
If $v$ lies within $\triangle p_1 p_2 p_3$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_1 p_2 p_3$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_1 + \angle p_2 = \angle p_3$.
Then a circle with radius $R(v) + \epsilon$ around $w$ such that $|v-w| < 2 \epsilon$ can only touch $p_1$ and $p_3$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
Bones added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
This means that walking up the graph from a marked region to a local maximum follows a single path without branching.
\end{proof}

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth]{sources/method/branch_upward_edge_property.pdf}
\caption{The radial distance can only increase along one edge around a branch point in the medial axis.}
\label{branch_upward_edge_property}
\end{figure}

>>>>

\begin{figure} \centering
\newlength{\significancePropertiesHeight}
\setlength{\significancePropertiesHeight}{.25\columnwidth}
\begin{subfigure}{0.35\columnwidth} \centering
\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_based_angles.pdf}
\caption{Significance}
\label{distance_based_angles}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth} \centering
\includegraphics[height=\significancePropertiesHeight]{sources/method/distance_ratio_limit.pdf}
\caption{Distance}
\label{distance_ratio_limit}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth} \centering
\includegraphics[height=\significancePropertiesHeight]{sources/method/branch_upward_edge_property.pdf}
\caption{Upward edge}
\label{branch_upward_edge_property}
\end{subfigure}
\caption{
Properties of feature radius $R$.
Part of outline shape in thick black,
skeleton in red,
inscribed circle in gray,
radii in dashed lines.
\subref{distance_based_angles} The significance measure can be simplified using $\alpha = 2 \gamma = 2 \cos^{-1} \Delta R / |v_1 - v_0|$.
\subref{distance_ratio_limit} The distance $|v_1 - v_0| > \Delta R$ because otherwise the feature radius would not be one of an inscribed circle.
\subref{branch_upward_edge_property} The radial distance can only increase along one edge around a branch point in the medial axis.
}
\end{figure}

@@

\begin{lemma}\label{single_upward_edge}
From any node in the graph which is not a saddle point there is at most a single edge going upward.
\end{lemma}
\begin{proof}
Any branch point $v$ in the MAT coincides with the circumcircle of its support $p_0, p_1, p_2$.
If $v$ lies within $\triangle p_0 p_1 p_2$ it is a local maximum and otherwise we will show it has exactly one upward edge.
If $v$ lies outside of $\triangle p_0 p_1 p_2$ then those support points lie within a \SI{180}{\degree} range from $v$
and one point lies in the middle, say $\angle p_0 + \angle p_1 = \angle p_2$.
Then a circle with radius $R(v) + \epsilon$ around $v'$ such that $|v-v'| < \epsilon$ can only touch $p_0$ and $p_2$.
See \cref{branch_upward_edge_property}.
%See VoronoiQuadrangulation::filterUnmarkedRegions
Bones added because of the trapezoidation always go down to $R=0$, so these don't change the property that each node has at most a single upward edge.
This means that walking up the graph from a marked region to a local maximum follows a single path without branching.
\end{proof}
